A 3d curvilinear skeletonization algorithm with application to bidirectional path tracing

### 2012-09-08 pathtracint_application_skeleton.tex
Mise à jour de la partie sur la résolution de la RE

$p$ is a probability density function that is used to sample $N$ samples $(\Phi_i)_{i = 1...N}$ of the hemisphere $\Omega_x$.

@@

% parler de la variance

>>>>

$p$ is a probability density function (pdf) that is used to sample $N$ samples $(\Phi_i)_{i = 1...N}$ of the hemisphere $\Omega_x$.

@@

The variance of the estimator express its quality. The lower the variance is, the better is the estimator. We have:

\begin{equation*}
\sigma^2[\langle L_r(x \rightarrow \Theta) \rangle] = \frac{1}{N} \int_{\Omega_x} (\frac{f(\Phi)}{p(\Phi)} - L_r(x \rightarrow \Theta))^2 d\omega_\Phi
\end{equation*}

Then if we increase the number of samples we decrease the variance and the estimator gives better results. Another way to decrease the variance is to choose a good pdf. Actually the best is to choose a pdf that match the shape of the function to integrate (ie. give high density to samples that have high values for the function and low density to samples that have low values).

This str	ategy of choosing a good pdf is called \myem{importance sampling} and is over-used in global illumination to improve the convergence of the algorithms.
